Title

### 2024-03-12 outputs/paper/paper.qmd
paper updated

This paper utilize data from open.alberta.ca as bases.

@@

Data used in this paper was cleaned and processed with the programming language R [@citeR]. Also with support of additional packages in R: `tidyverse` [@citeTidyverse], `ggplot2` [@citeGgplot], `janitor` [@citeJanitor], `dplyr` [@citeDplyr], `readr` [@citeReadr], `knitr` [@citeknitr], 'kableExtra' [@citeKableExtra], 'reshape2' [@citeReshape2].

@@

>>>>

@@

Data used in this paper was cleaned and processed with the programming language R [@citeR]. Also with support of additional packages in R: `tidyverse` [@citeTidyverse], `ggplot2` [@citeGgplot], `janitor` [@citeJanitor], `readr` [@citeReadr], `knitr` [@citeKnitr], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModelsummary].

@@

This paper utilize data from open.alberta.ca [@citeDatasource] as bases.
